Analysis PPM-S

### 2020-06-01 production/prod_analysis-cfa.rmd
Todo listo
Ya estan listas las tablas con los titulos y los demas detalles de formato

nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception networks",
              "Preference effort","Preference talent","Preference rich family","Preference networks",
              "Perception meritocratic","Perception non meritocratic","Preference meritocratic","Preference non meritocratic")

>>>>

nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception contacts",
              "Preference effort","Preference talent","Preference rich family","Preference contacts",
              "Perception meritocratic","Perception non meritocratic","Preference meritocratic","Preference non meritocratic")
